Future challenges for Research Software Engineering

### 2025-04-16 future_challenges_for_RSEng.tex
some color and structuring boxes

% Required packages
% =================
% Your \usepackage commands go here.
\usepackage{fancybox,framed}
\usepackage{footnote}
\makesavenoteenv[FramedParagraphWithFootnotes]{framed} % for author notes

@@

\subsection{What are new tasks of RTPs?}
FG-NOTE: RSEs are one type of specialization of RTPs ins science. Do we see any other?

\subsection{Impact of Alternate Career Paths for Researchers on the Structure of Research Institutes}
FG-NOTE: By Nick. I've put it here, due to the realtion with the RTP question.

>>>>

% Required packages
% =================
% Your \usepackage commands go here.
\usepackage{fancybox,framed}
\usepackage{footnote}
\makesavenoteenv[FramedParagraphWithFootnotes]{framed} % for author notes
\usepackage{color}
\usepackage[dvipsnames]{xcolor}
\usepackage[most]{tcolorbox}

\newtcbtheorem[number within=section]{whatis}{What is 2035}{
  enhanced,
  segmentation engine=empty,
%  beamer,
fuzzy shadow={2mm}{-1mm}{0mm}{0.1mm}%
{black!50!white},
  sharp corners,
  attach boxed title to top left={
    yshifttext=-1mm
  },
%  halign lower=flush center,
  colback=white,
  colframe=Maroon!75!white,
  fonttitle=\bfseries,
  attach boxed title to top left={yshift=-2mm,xshift=3mm},
  fontlower=\itshape,
  boxed title style={
    sharp corners,
    size=small,
    colback=Maroon!75!black,
    colframe=Maroon!75!black,
  } 
}{ist}

\newtcbtheorem[number within=section]{story}{Story}{
  enhanced,
  segmentation engine=empty,
%  beamer,
fuzzy shadow={2mm}{-1mm}{0mm}{0.1mm}%
{black!50!white},
  sharp corners,
  attach boxed title to top right={
    yshifttext=-1mm
  },
%  halign lower=flush center,
  colback=white,
  colframe=ForestGreen!75!white,
  fonttitle=\bfseries,
  attach boxed title to top right={yshift=-2mm,xshift=3mm},
  fontlower=\itshape,
  boxed title style={
    sharp corners,
    size=small,
    colback=ForestGreen!75!black,
    colframe=ForestGreen!75!black,
  }
}{str}

@@

\subsection{What are new tasks of RTPs?}
\begin{story}{text 1 }{text 2}
 FG-NOTE: RSEs are one type of specialization of RTPs ins science. Do we see any other?
\end{story}

\subsection{Impact of Alternate Career Paths for Researchers on the Structure of Research Institutes}
\begin{whatis}{text 1 }{text 2}
FG-NOTE: By Nick. I've put it here, due to the realtion with the RTP question.
\end{whatis}
